---
title: "FinalExamMarkdownTest"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
```

## Final Exam Markdown Test

The IST722 final exam has two parts. The first part, which will be acocmplished in class,
will involve using a markdown file to produce diagnostics, graphs, and statistical output
for your report. Obviously you will need your laptop to be able to do this. Just before the exam
I will provide a template Rmd file to which you will add your own analytical choices. I will also provide your own custom datasets. At the end of that class session, you will submit 
a "knitted" version of your output to Blackboard. This output will then be the sole 
basis of your final report.

This file provides a preview of the Rmd file you will receive for the exam. When you click 
the **Knit** button at the top of the code window an html document will be generated that
includes both content as well as the output of any embedded R code chunks within the 
document. You can embed an R code chunk like this:

```{r summary}
summary(mtcars)
```

## Including Plots for your Report

Your report will be enhanced by providing helpful graphs that support the arguments you
are trying to make about your data. Code elements in a markdown file can be used to create
graphs that will appear in your html output. For example:

```{r plot, echo=FALSE}
boxplot(mpg ~ am, data=mtcars)
```

Note that the `echo = FALSE` parameter was added to the previous code chunk to prevent 
printing of the R code that generated the plot. This is a stylistic choice, but it should
generally be avoided for the final exam, because you (and I) will want to have a clear
record of the commands you used to generate your output.

One very important aspect of doing your final exam in this format is that you will have to
plan in advance what analyses you will need to conduct. So one of your main tasks during the
final class session will be to choose appropriate analyses for your output. For example, the
following code produces results for both a t-test and a regression analysis.

```{r tests, echo=FALSE}
t.test(mpg ~ am, data=mtcars)
summary(lm(mpg ~ hp + wt + gear, data=mtcars))
```

Click the **Knit** button to create and inspect your html document. If the knitting process 
is successful an html file will be submitted to your current working directory. 
Find that file and submit it to the dropbox on Blackboard to show that you have 
successfully completed this process.